\LARGE \bf TODO Name this thing

### 2012-02-18 papers/itsc_2012/root.tex
finished related work section

\section{INTRODUCTION}

@@

The arrival of driver-less cars presents a number of challenges that need to addressed in the near term. Road infrastructure needs to be updated to better support autonomous vehicles. A number of laws and safety concerns need to be addressed in the context of driver-less cars. Human drivers need new methodologies to interact with autonomous drivers on public roads. At the same time, driver-less cars provide opportunities of solving traffic problems in ways that were never before possible. For instance, autonomous cars can be quickly diverted to make way for emergency vehicles responding to an accident. Even day-to-day traffic issues such as congestion could potentially be greatly reduced by effective management of traffic flow. This work attempts to address some of these problems.

@@

This paper introduces an open source multi-agent traffic micro-simulator called AORTA, which stands for \textit{Approximately Orchestrated Road Traffic Automata}. The AORTA simulator focuses on the interactions between individual vehicles and intersections, both of which act as \textit{agents} in AORTA's framework. Vehicles interact with other vehicles to pass and change lanes, and interact with intersections to decide when to cross them. Researchers developing applications on top of the AORTA simulator define \textit{behaviors} that these agents follow to interact with one another. To optimize traffic flow, external \textit{overseers} can coordinate with these agents to provide recommendations such as route suggestions or intersection signaling policies. An advantage of such an approach is that by assigning human-like behaviors such as the "car following model" \cite{brackstone1999car} to vehicles and traffic signal like policies to intersection, AORTA can just as easily simulate human traffic.

Like any other traffic micro-simulator \commentpk{check this term}, AORTA needs maps to run simulations. We generate our maps using road data available from OpenStreetMap (OSM) \cite{osm}, a Wikipedia like interface for world maps. Researchers using AORTA can export the relevant map area from OSM that is then parsed by AORTA to create scale simulations of the real world. Using real world road data is advantageous for a number of reasons. First, researchers using AORTA for human traffic simulations would find it advantageous to also have the ability to use real-world roads. Second, even as infrastructural changes will be made to the road infrastructure to accommodate driver-less cars, it is reasonable to assume that the \textit{same} road network will still be in use. Third, using real-world data from OSM allows setting up simulations for an area of interest in a matter of minutes, thereby allowing easy transfer of research results to any desired region.

@@

\section{RELATED WORKS}

\commentpk{This section is still under construction. Do not review.}

A number of good micro-simulators have been created in the past decade. In this section we compare some of the similarities and differences with other such simulators.

One such

>>>>

\section{INTRODUCTION}
\label{sec:introduction}

@@

The arrival of driver-less cars presents a number of challenges that need to addressed in the near term. Road infrastructure needs to be updated to better support autonomous vehicles. A number of legal and safety concerns need to be addressed in the context of driver-less cars. Human drivers need new methodologies to interact with autonomous drivers on public roads. At the same time, driver-less cars provide opportunities of solving traffic problems in ways that were never before possible. For instance, autonomous cars can be quickly diverted to make way for emergency vehicles responding to an accident. Even day-to-day traffic issues such as congestion could potentially be greatly reduced by effective management of traffic flow. This work attempts to address some of these problems.

@@

This paper introduces an open source multi-agent microscopic traffic simulator called AORTA, which stands for \textit{Approximately Orchestrated Road Traffic Automata}. The AORTA simulator focuses on the interactions between individual vehicles and intersections, both of which act as \textit{agents} in AORTA's framework. Vehicles interact with other vehicles to pass and change lanes, and interact with intersections to decide when to cross them. Researchers developing applications on top of the AORTA simulator define \textit{behaviors} that these agents follow to interact with one another. To optimize traffic flow, external \textit{overseers} can coordinate with these agents to provide recommendations such as route suggestions or intersection signaling policies. An advantage of such an approach is that by assigning human-like behaviors such as the "car following model" \cite{brackstone1999car} to vehicles and traffic signal like policies to intersection, AORTA can just as easily simulate human traffic.

Like any other microscopic traffic simulator, AORTA needs maps to run simulations. We generate our maps using road data available from OpenStreetMap (OSM) \cite{osm}, a Wikipedia like interface for world maps. Researchers using AORTA can export the relevant map area from OSM that is then parsed by AORTA to create scale simulations of the real world. Using real world road data is advantageous for a number of reasons. First, researchers using AORTA for human traffic simulations would find it advantageous to also have the ability to use real-world roads. Second, even as infrastructural changes will be made to the road infrastructure to accommodate driver-less cars, it is reasonable to assume that the \textit{same} road network will still be in use. Third, using real-world data from OSM allows setting up simulations for an area of interest in a matter of minutes, thereby allowing easy transfer of research results to any desired region.

@@

\section{RELATED WORK}
\label{sec:related_work}

Computational processing power has made excellent advancements in the last two decades. Parallel computing has proved significant for traffic simulation through the use of Geographic Information System (GIS) software \cite{pursula1999simulation}. Advanced computing techniques have enabled microscopic models of traffic simulation to generate results at a meaningful scale (city-wide or greater). As a result, a number of good micro-simulators have come up in the past decade. We review a number of such simulators in this section along with other relevant work.

A number of traffic simulators already make use of OSM data. MATSim is one such multi-agent simulator that focuses on performing large-scale simulations in a relatively small amount of time \cite{balmer2009matsim}. Traffic demand is supplied to MATSim in the form of \textit{plans} that an individual may intend to follow in a given day. MATSim aims to iteratively improve these plans though offline computation to maximize traffic throughput. In other words, it helps individuals understand the best way to go about their daily routine to minimize time spent in transit. This goal is somewhat different from that of AORTA, where the demand supplied by individuals is taken as is. Instead, AORTA aims to reduce traffic congestion through interactions with individuals in real-time based on the current demand.

Another popular open source traffic simulator that can use OSM data is SUMO \cite{SUMO2011}, which shares the same goals as AORTA and is fairly similar at a high level. SUMO has been used to study the effect of automated transportation systems, route planning of individual vehicles, as well as dynamically adapting traffic signal policies to increase traffic efficiency. AORTA and SUMO differ in the manner in which intersections are handled. SUMO uses traditional traffic signals, while AORTA adopts a much more general \textit{reservation} system. A reservation tells a car when it is safe to take its desired path through the intersection. Reservations can be alotted to vehicles through more traditional means such as traffic signals or stop-sign based intersection based precedence, or through more efficient methods designed specificaly for autonomous intersection management \cite{JAIR08-dresner}. \commentpk{does this difference seem a bit pedantic?}

On the other hand, there are a number of simulators that specifically target autonomous traffic systems. One such system is AIM \cite{JAIR08-dresner}, which aims to optimize traffic flow between autonomous vehicles at a given intersection. AIM studies problems at the scale of a single intersection, while AORTA has the potential to apply some of the same research at a city-wide scale to real-world road networks. A few simulators focus on autonomous vehicles with sensors and actuators \cite{figueiredo2009approach}. These simulators are used to ensure that autonomous vehicles are behaving correctly while interacting with other vehicles and infrastructure. On the other hand, AORTA assumes that autonomous vehicles are capable of reasonable driving, and focuses on interactions between agents to optimize traffic flow.

Autonomous agents have also been used in the past to model human traffic as well. For instance, an approach models human merging and lane changing behavior through the use of autonomous agents interacting with one another \cite{hidas2002modelling}. Another approach attempted to improve traffic congestion for human drivers by using a network of autonomous intersection. These intersections have the ability to interact with one another and execute a dynamic traffic signal policy minimizing overall wait time \cite{manikonda2001autonomous}.

\commentpk{I suspect there are still more papers that might be more relevant - we'll definitely have some when we write the application}

% In the realm of applications
% It is also necessary to analyze some other simulators that use GIS data for microscopic traffic simulations, this is because it may be possible to export OSM data so that it can be used by these simulators, though the authors are not aware of such a connection. Incident response has been studied by the following paper (though perhaps only a minor citation as it is an application and does not really compare against AORTA, but it is something we would like to study this as well. \cite{huang2007gis}
